---
title: "simpleRegress"
author: "Amy Estrada"
date: "Spring 2021"
output: 
    html_document:
        toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Bears regression model

### make a simple regression model-read in the data

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

# NECK
## Model LENGTH ~ NECK  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
new <- data.frame(NECK=c(16,28,31))
predict(simp,new,se.fit=TRUE)
```


# HEADWTH
## Model LEGTH ~ HEADWTH

```{r}
simpHW <-lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simpHW)
summary.lm(simpHW)
```

```{r}
new <- data.frame(HEADWTH=c(5.5,9,8))
predict(simpHW,new,se.fit=TRUE)
```

# HEADLEN
## Model LEGTH ~ HEADLEN

```{r}
simpHL <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simpHL)
summary.lm(simpHL)
```

```{r}
new <- data.frame(HEADLEN=bears$HEADLEN [c(16,28,31)])
predict(simpHL,new,se.fit=TRUE)
```

# WEIGHT

```{r}
simpW <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simpW)
summary.lm(simpW)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
newData <- data.frame(HEADLEN=c(17,13,9))
predict(simpHL,newData,se.fit=TRUE)
```


## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


